### 2019-07-19 thesis.tex
*** empty log message ***

\chapter{Applications to astrophysical plasmas}
\label{appD}
On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and practically inexhaustible energy
source once we have controlled and energetically efficient thermonuclear fusion
\cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
to the occurrence of lightning during storms, flames, and the beautiful auroras
that take place at high latitudes. In the space, however, the situation is the
opposite. Starting in the outer layers of Earth's atmosphere, passing through the
solar wind in the interplanetary space, to the stellar interiors and atmospheres,
accretion disks, and molecular clouds it is estimated that something around
$99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
\cite{may}.

Plasma is a gas in which the atoms -or molecules- are in an ionized state.
In such condition, long-range electric and magnetic forces determine the
interactions of the charged particles. This coupling between the variations
in the electric and magnetic fields and the motion of ions and electrons
is the cause of the wide variety of oscillatory processes that characterize
the plasma dynamics\cite{tsytotp}.

Understanding the complex physics of
the plasma state is a fundamental

>>>>

\chapter{Applications to astrophysical plasmas}
\label{appD}
On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and practically inexhaustible energy
source once we have controlled and energetically efficient thermonuclear fusion
\cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
to the occurrence of lightning during storms, flames, and the beautiful auroras
that take place at high latitudes. In the space, however, the situation is the
opposite. Starting in the outer layers of Earth's atmosphere, passing through the
solar wind in the interplanetary space, to the stellar interiors and atmospheres,
accretion disks, and molecular clouds it is estimated that something around
$99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
\cite{may}. Therefore, the study of the physics of plasma processes is a
fundamental branch of astrophysics\cite{tsypa}.

Space plasmas are observed in a vast range of temperature, density, magnetic
field strengths and scale lengths. However, in most of the cases, models used
to describe processes

%Plasma is a gas in which the atoms -or molecules- are in an ionized state.
% In such condition, long-range electric and magnetic forces determine the
% interactions of the charged particles. This coupling between the variations
% in the electric and magnetic fields and the motion of ions and electrons
% is the cause of the wide variety of oscillatory processes that characterize
% the plasma dynamics\cite{tsytotp}.
